On Secure Delegation of SampBQP with a Classical Client

### 2020-02-09 bqp.tex
Make another editorial pass

We then apply the recent result parallel repetition get negligible soundness again:

\begin{protocol}{Parallel repetition of \cref{proto:QPIP0BQP}}
	\label{proto:repQPIP0BQP}
	\Ethan{TODO PROOFREAD ME}
	Run $m=\poly(n)$ copies of \cref{proto:QPIP0BQP} in parallel. Accept if the proportion of accepted copies is over some certain threshold $p(n)\in(0, 1)$.

\end{protocol}

\begin{thm}
	\cref{proto:repQPIP0BQP} has negligible completeness and soundness
\end{thm}
\begin{prf}
	See \cite{parallelrep, alagic2019twomessage}
\end{prf}

@@

	By the soundness of $\Pibzrep$, $v_{i, b}=acc$ implies that $x\in L_{i, b}\Rightarrow f_i(x)=b$ with overwhelming probability.
	In other words, $y_i$ is correct with probability $1-\varepsilon_i$ where $\varepsilon_i=\negl(n)$.

>>>>

We use the recent results \cite{parallelrep, alagic2019twomessage} to apply parallel repetition to $\Pibz$ to get $\Pibzrep$ which has negligible soundness.

\Ethan{Is the following even necessary?}

\begin{protocol}{Parallel repetition of \cref{proto:QPIP0BQP}}
	\label{proto:repQPIP0BQP}
	\Ethan{TODO PROOFREAD ME}
	Run $m=\poly(n)$ copies of \cref{proto:QPIP0BQP} in parallel. Accept if the proportion of accepted copies is over some certain threshold $p(n)\in(0, 1)$.
\end{protocol}

\begin{thm}
	\cref{proto:repQPIP0BQP} has negligible completeness and soundness and is blind.
\end{thm}
\begin{prf}
	See \cite{parallelrep, alagic2019twomessage}
\end{prf}

@@

	By the soundness of $\Pibzrep$, $v_{i, b}=acc$ implies that $x\in L_{i, b}$ with overwhelming probability.
	In other words, $y_i$ is correct with probability $1-\varepsilon_i$ where $\varepsilon_i=\negl(n)$.
